This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-07 article.tex
Fixed some punctuation

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
To come at the exact weight of things= in the scientific steel-yard, the fulchrum, [Walter Shandy] would say, should be almost invisible, to avoid all friction from popular tenets=,---without this= the minuti\ae\ of philosophy, which should always= turn the balance, will have no weight at all---Knowledge, like matter, he would affirm, was= divisible in infinitum---that the grains= and scruples= were as= much a part of it, as= the gravitation of the whole world.
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\end{tikzpicture}
\end{center}}

>>>>

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
To come at the exact weight of things= in the scientific steel-yard, the fulchrum, [Walter Shandy] would say, should be almost invisible, to avoid all friction from popular tenets=;---without this= the minuti\ae\ of philosophy, which should always= turn the balance, will have no weight at all. Knowledge, like matter, he would affirm, was= divisible in infinitum;---that the grains= and scruples= were as= much a part of it, as= the gravitation of the whole world.
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\end{tikzpicture}
\end{center}}
